---
title: "Assignment_1"
author: "Xiru Lyu"
date: "1/22/2018"
output:
  pdf_document: default
---

## Problem 1: Create the Vectors

### (a) (1,2,3,...,19,20)
```{r}
seq(from=1, to=20)
```

### (b) (20,19,...,2,1)
```{r}
seq(from=20, to=1)
```

### (c) (1,2,3,...,19,20,19,18,...,2,1)
```{r}
c(1:20,19:1)
```

### (d) (4, 6, 3) and assign it to the name tmp.
```{r}
tmp <- c(4,6,3)
tmp
```

### (e) (4,6,3, 4,6,3,...,4,6,3) where there are 10 occurrences of 4.
```{r}
rep(tmp,times=10)
```

### (f) (4,6,3, 4,6,3,...,4,6,3,4) where there are 11 occurrences of 4, 10 occurrences of 6 and 10 occur- rences of 3.
```{r}
c(rep(tmp,length=31))
```

### (g) (4,4,...,4, 6,6,...,6, 3,3,...,3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r}
c(rep(tmp[1],times=10),rep(tmp[2],times=20),rep(tmp[3],times=30))
```


## Problem 2: Create a vector of the values of ex cos(x) at x = 3,3.1,3.2,...,6.

```{r}
x <- seq(from=3, to=6, by=0.1)
exp(x)*cos(x)
```


## Problem 3: Create the following vectors

### (a)
```{r}
a <- seq(from=3,to=36,by=3)
b <- seq(from=1,to=34,by=3)
0.1^a*0.2^b
```

### (b)
```{r}
c <- seq(from=1,to=25)
2^c/c
```


## Problem 4: Calculate the following

### (a)
```{r}
i_1 <- seq(from=10, to=100)
sum(i_1^3+4*i_1^2)
```

### (b)
```{r}
i_2 <- seq(from=1, to=25)
sum((2^i_2/i_2)+(3^i_2/i_2^2))
```


## Problem 5: Use the function *paste* to create the following character vectors of length 30

### (a) ("label 1", "label 2", ....., "label 30").
```{r}
paste(c("label"), 1:30)
```

### (b) ("fn1", "fn2", ..., "fn30").
```{r}
paste(c('fn'), 1:30, sep="")
```


## Problem 6

```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)

n <- seq(from=2,to=250)
```

### (a) Create the vector
```{r}
yVec[n]-xVec[n-1]
```

### (b) Create the vector
```{r}
sin(yVec[n-1])/cos(xVec[n])
```

### (c) Create the vector
```{r}
k <- seq(from=3,to=250)
xVec[k-2]+2*xVec[k-1]-xVec[k]
```

### (d) Calculate the value
```{r}
m <- seq(from=1,to=249)
sum(exp(-xVec[m+1])/(xVec[m]+10))
```


## Problem 7

### (a) Pick out the values in yVec which are > 600.
```{r}
yVec[yVec>600]
```

### (b) What are the index positions in yVec of the values which are > 600?
```{r}
w <- which(yVec>600)
w
```

### (c) What are the values in xVec which correspond to the values in yVec which are > 600?
```{r}
xVec[w]
```

### (d) Create the vector
```{r}
num <- seq(from=1,to=250)
abs(xVec[num]-mean(xVec))^(1/2)
```

### (e) How many values in yVec are within 200 of the maximum value of the terms in yVec?
```{r}
length(yVec[yVec<=max(yVec)+200 & yVec>=max(yVec)-200])
```

### (f) How many numbers in xVec are divisible by 2?
```{r}
length(xVec[xVec%%2==0])
```

### (g) Sort the numbers in the vector xVec in the order of increasing values in yVec.
```{r}
xVec[order(yVec)]
```

### (h) PickouttheelementsinyVecatindexpositions1,4,7,10,13,....
```{r}
index <- seq(from=1, to=250,by=3)
yVec[index]
```


## Problem 8: Calculation
```{r}
u <- seq(from=2, to=38, by=2)
d <- seq(from=3, to=39, by=2)
sum(cumprod(u/d))+1
```

